### 2025-12-09 acronyms/acronyms.tex
double fix
cisf
ITEST

@@

\newacronym{sca}{SECA}{Simultaneous Evaluation of Criteria and Alternatives}

@@

>>>>

\newacronym{ihl}{IHLRWM}{International High Level Radioactive Waste Management}

@@

\newacronym{sea}{SECA}{Simultaneous Evaluation of Criteria and Alternatives}

@@

\newacronym{its}{ITEST}{Innovative Technology Experiences for Students and Teachers}
